\documentclass[letterpaper, 11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\setlist[itemize]{left=0pt}

\begin{document}

\thispagestyle{empty}

%----------------%
%  CONTACT INFO  %
% ---------------%

\begin{center}
    {\LARGE \textbf{William Wingate}} \\
    \vspace{10pt}
    \textit{wtwingate@gmail.com | (304) 701-0577 | github.com/wtwingate |
    linkedin.com/in/wtwingate}
\end{center}

%-----------%
%  SUMMARY  %
%-----------%

\section*{Summary}
Junior full-stack developer with two years of experience in building and
maintaining websites using modern web technologies, including HTML, CSS,
JavaScript, Python, and Ruby.  Skilled in optimizing website functionality,
enhancing user experience, and prioritizing performance and accessibility.
Proficient in web design, back-end development, and database management.
Seeking a full-stack developer role to further develop my programming craft
while collaborating with a skilled and dynamic team.

%----------%
%  SKILLS  %
%----------%

\section*{Skills}
\begin{itemize}
    \item \textbf{Languages:} C, C++, Java, JavaScript, TypeScript, Python,
        Ruby, Bash, SQL, HTML, CSS
    \item \textbf{Frameworks:} React, Express, Next.js, Astro, Django, Ruby on
        Rails, Tailwind CSS
    \item \textbf{Technologies:} Linux/Unix, Node.js, Git, Docker, PostgreSQL,
        RESTful APIs
    \item \textbf{Methodologies:} Object-Oriented Programming (OOP), Agile
        Software Development, System Design, Test-Driven Development (TDD)
\end{itemize}

%--------------%
%  EXPERIENCE  %
%--------------%

\section*{Experience}
\textbf{Full-Stack Developer}
\hfill \textit{Mallard Web Design} \\
\textit{October 2024 — Present}
\hfill \textit{Summersville, WV}
\begin{itemize}
    \item Started my own company to provide custom websites for local
        businesses.
\end{itemize}

\noindent
\textbf{Full-Stack Developer Intern}
\hfill \textit{Horizon Investments} \\
\textit{June 2024 — August 2024}
\hfill \textit{Charlotte, NC}
\begin{itemize}
    \item Worked with senior developers to build and maintain a full-stack
        financial planning web app.
    \item Refactored and redesigned multiple pages to enhance UI/UX and improve
        site performance.
    \item Discovered and fixed a major security vulnerability in our use of
        third-party code.
    \item Normalized database by refactoring schema and consolidating duplicate
        data.
\end{itemize}

\noindent
\textbf{Music Director}
\hfill \textit{All Saints Church} \\
\textit{August 2017 — October 2024}
\hfill \textit{Weddington, NC}
\begin{itemize}
    \item Designed and maintained church website while overseeing church music
        and media.
    \item Developed a web application for the Anglican lectionary to streamline
        liturgical service planning.
\end{itemize}

%-------------%
%  EDUCATION  %
%-------------%

\section*{Education}
\textbf{Bachelor of Science in Religion}
\hfill \textit{Liberty University} \\
\textit{September 2009 — May 2013}
\hfill \textit{Lynchburg, VA}

\end{document}
